Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-09 snapshot_system/eval1.tex
update exper

Figure~\ref{fig-exbin-efficiency-graph} shows the deduplication efficiency which is
the percent of deduped duplicate chunks by SRB and VC.
It also lists several PDS sizes chosen for VC. ``2\% PDS" means that
we allocate the space of distributed shared memory  to accommodate $\delta=2\%$
of data chunks shared among VMs. Namely 
With $\delta=2\%$, the deduplication efficiency can reach over 90\% 
while $\delta=4\%$, the deduplication efficiency can reach over 92\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support PDS.  
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
for global comparison.
In all cases, VC provides similar or better deduplication efficiency than SRB.

\comments{%both of the bar charts are superceded by the graph below
%\comments{
    %this version of the figure is vertical
    \begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            ybar,
            bar width=1.00cm,
            symbolic x coords={SRB,VC},
            xlabel={Algorithm},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            xtick=data, %without this the symbolic coords may be repeated as filler
            enlarge x limits=0.6, %used to push plots towards center
            ymin=85,
            %ymax=100,
            nodes near coords,
            nodes near coords align={vertical},
            ]
            \addplot coordinates {(SRB,89.99) (VC,90.51)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
  \label{fig-exbin-efficiency1}
\end{figure}
%}
%same figure as above but horizontal (better for only two data points)
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            xbar,
            width=7cm,
            height=3.5cm,
            %bar width=0.75cm,
            symbolic y coords={SRB,VC},
            xlabel={Dedup. Efficiency (\%)},
            %ylabel={Algorithm},
            %extra x ticks={4.5,5.5,6.5} %to add extra ticks
            ytick=data, %without this the symbolic coords may be repeated as filler
            enlarge y limits=0.5,
            xmin=85,
            xmax=92, %otherwise label overlaps with right border
            nodes near coords,
            nodes near coords align={horizontal},
            ]
            \addplot coordinates {(89.99,SRB) (90.51,VC)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
  \label{fig-exbin-efficiency2}
\end{figure}
}

%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot[color=blue,mark=none] table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dotted, color=red,mark=none] table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \addplot[loosely dotted, color=brown,mark=none] table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dashed,color=black,mark=none] table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC (1\%CDS),VC (2\%CDS),VC (4\%CDS)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    Stateless Routing with Binning and VC.}
  \label{fig-exbin-efficiency-graph}
\end{figure}

Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication on dataset1.
The X axis shows the overall impact in (a),  impact on OS disks in (b), and impact on data disks in (c).
Each bar in the Y axis shows the data size after deduplication divided by the original data size.
Level-1 elimination can reduce the data size to about 23\% of original data, namely it delivers close 77\% reduction.
Level-2 elimination is applied to data that could pass level-1, it
reduces the size further to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
Level-3 elimination together with level 1 and 2
reduces the size further to 8\% of original size, namely it delivers additional 10.5\% reduction.
Level 2 elimination is more visible in OS disk than data disk, because data change frequency is really small
when we sample last 10 snapshots of each user in 10 days. Nevertheless, the overall impact of level 2 is still significant.
A 4.5\% of reduction from the original data represents about 450TB space saving for a 1000-node cluster.

@@

%To see the impact of multi-level deduplication on different OS releases,
%Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
Figure~\ref{fig:oscds} shows the impact of different levels of deduplication for different OS releases.
In this experiment, we tag each block in 350 OS disk snapshots from dataset1 as  ``new''
if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot store;
``CDS''  if this block can be found  in CDS;
``Parent segment'' if  this block is marked unchanged in parent's segment recipe.
``Parent block'' if  this block is marked unchanged in parent's block recipe.
With this tagging, we compute the percentage of deduplication accomplished by each level.
As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination,
this is because the time interval between two snapshots in our dataset
is quite short and the Aliyun cloud service makes a snapshot  everyday  for each VM.
On the other hand,  CDS still finds lots of duplicates that inner VM deduplication can't find,
contributing about 10\% of reduction on average.

It is noticeable that level-1 deduplication doesn't work well for CentOS, a significant percentage of data is not
eliminated until they reach level-3. It shows that even user upgrade his VM system heavily and frequently
such that data locality is totally lost, those OS-related data can still be identified at level-3.

In general we see a stable data reduction ratio for all OS varieties, ranging from 92\% to 97\%, that means
the storage cost of 10 full snapshots combined is still smaller than the original disk size. And compare to 
today's widely used copy-on-write snapshot technique, which is similar to our level-1 deduplication, our
solution cut the snapshot storage cost by 64\%.

@@

\subsection{System Performance}
{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
evaulate the system performance on the second snapshot backup. We repeat such procedure
under different CDS memory usage settings, the results of backup time break down are shown in
Figure~\ref{fig:single_vm_backup}.

@@

It's easy to see that the time of I/O dominates the backup process, our deduplication
procedure only takes a tiny fraction of the total backup time. Larger memory permits us to
use larger CDS index to cover more of global index, as a result the amount of data to be writen
is reduced and so do the writing time.
Inside the deduplication procedure, the time costs of level-1
is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
because the number of fingerprints to process are just the same.

{\bf Parallel VM Backup} We then evaluate the performance of writing snapshots in parallel.
To begin, on each node we let 4 VMs writing snapshot concurrently, and gradually 
increase number of VMs to 12 to saturate our system capability. We observed 
the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
which is far beyond our QFS file system capability. The reason behind it is our efficient
deduplication architecture and compression greatly reduce the amount of data that need to be writen to
the file system. The main bottleneck here is our QFS only manages one disk per node, 
making it inefficient to utilize the benefits of parallel disk access. We expect our achitecture can
perform even better in production cluster which normally has more than ten disks on each node.

In Figure~\ref{fig:srb_vs_vc} you
can see simulated backup times using actual throughput numbers from our test
backup cluster, and VC outperforms SRB mainly due to significantly fewer index
lookups (since SRB uses hash-partitioning, all lookups are essentially random
and caching will be largely innefective).  \emph{Should we use one of the two
bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
charts in the paper until we decide? If we use the bar charts some text will
have to be changed. We could also add each of the CDS sizes to the bar chart
and have 4 bars instead of 2.}

>>>>

Figure~\ref{fig-exbin-efficiency-graph} shows the deduplication efficiency which is
the percent of deduped duplicate chunks by SRB and VC.
It also lists several PDS sizes chosen for VC. ``2\% PDS" means that
we allocate the space of distributed shared memory  to accommodate $\delta=2\%$
of data chunks shared among VMs. Namely 
With $\delta=2\%$, the deduplication efficiency can reach over 90\% 
while $\delta=4\%$, the deduplication efficiency can reach over 92\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support PDS.  
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
for global comparison.
In all cases, VC provides similar or better deduplication efficiency than SRB

This shows VC can remove  a competitive amount of duplicates.
In general, our experiment shows that
dirty-bit detection in the segment level  can reduce the data size to about 23\% of original data, 
which leads  about 77\% reduction.
Local search within a segment can   further reduce the data size
to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
The PDS-based cross-VM detection with $\delta=2\% $
can reduce the  size further to 8\% of original size, namely it 
delivers additional 10.5\% reduction.

\comments{%both of the bar charts are superceded by the graph below
%\comments{
    %this version of the figure is vertical
    \begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            ybar,
            bar width=1.00cm,
            symbolic x coords={SRB,VC},
            xlabel={Algorithm},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            xtick=data, %without this the symbolic coords may be repeated as filler
            enlarge x limits=0.6, %used to push plots towards center
            ymin=85,
            %ymax=100,
            nodes near coords,
            nodes near coords align={vertical},
            ]
            \addplot coordinates {(SRB,89.99) (VC,90.51)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
         of SRB  and VC with $\delta=2\%$.}
        %($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
  \label{fig-exbin-efficiency1}
\end{figure}
%}
%same figure as above but horizontal (better for only two data points)
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            xbar,
            width=7cm,
            height=3.5cm,
            %bar width=0.75cm,
            symbolic y coords={SRB,VC},
            xlabel={Dedup. Efficiency (\%)},
            %ylabel={Algorithm},
            %extra x ticks={4.5,5.5,6.5} %to add extra ticks
            ytick=data, %without this the symbolic coords may be repeated as filler
            enlarge y limits=0.5,
            xmin=85,
            xmax=92, %otherwise label overlaps with right border
            nodes near coords,
            nodes near coords align={horizontal},
            ]
            \addplot coordinates {(89.99,SRB) (90.51,VC)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between Stateless Routing with Binning and VC with 2\% CDS.}
  \label{fig-exbin-efficiency2}
\end{figure}
}

%graph comparing extreme binning (SRB) with CDS model (VC) for different cds percentages
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot[color=blue,mark=none] table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dotted, color=red,mark=none] table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \addplot[loosely dotted, color=brown,mark=none] table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            \addplot[densely dashed,color=black,mark=none] table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \legend{SRB,VC (1\%CDS),VC (2\%CDS),VC (4\%CDS)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$) comparison between
    SRB and  VC.}
  \label{fig-exbin-efficiency-graph}
\end{figure}

@@

%To see the impact of multi-level deduplication on different OS releases,
%Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on

@@

\subsection{Processing Time and Throughput}
%{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
%backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
%scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
%evaulate the system performance on the second snapshot backup. We repeat such procedure
%under different CDS memory usage settings, the results of backup time break down are shown in

Figure~\ref{fig:srb_vs_vc} shows
the  average  processing  time of  each segment using VC and SRM in handling our dataset.
It has a breakdown of time for reading data and updating the metadata, network latency to visit
a remote machine, and index access for finger printer comparison.
SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
it relies on this local machine to access its index (often on the disk) and perform comparison.
VC is faster for index access because it conducts in-memory local search first and then
accesses  the PDS which is on distributed shared memory.  
SRB spends  slighter more time in  reading data and update because it also updates the on-disk
local meta data index.
Overall speaking,  VC is faster than SRB while data reading dominates the processing time. 
%all lookups are essentially random and caching will be largely innefective).

%\emph{Should we use one of the two
%bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
%charts in the paper until we decide? If we use the bar charts some text will
%have to be changed. We could also add each of the CDS sizes to the bar chart
%and have 4 bars instead of 2.}

Figure~\ref{fig:single_vm_backup} reports the average bacup time for a VM with VC with a varying number
of PDS size.
Again it shows that data reading dominates the backup process, our deduplication
procedure only takes a small fraction of the total backup time. 
The change of $\delta$ does not significantly affects the overall time and
PDS lookup takes a small amount of time.
%Larger memory permits us to
%use larger CDS index to cover more of global index, as a result the amount of data to be writen
%is reduced and so do the writing time.
%Inside the deduplication procedure, the time costs of level-1
%is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
%because the number of fingerprints to process are just the same.

@@

    Figure~\ref{fig:parallel_backup} shows the node throughput when all machine nodes run
the backup procedure in parallel.
To begin, on each node we let 4 VMs writing snapshot concurrently, and gradually 
increase number of VMs to 12 to saturate our system capability. We observed 
the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
which is far beyond our QFS file system capability. The reason behind it is our efficient
deduplication architecture and compression greatly reduce the amount of data that need to be written to
the file system. The main bottleneck here is our QFS only manages one disk per node, 
making it inefficient to utilize the benefits of parallel disk access. We expect our architecture can
perform even better in production cluster which normally has more than ten disks on each node.
